%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
  {Blockchain Engineer} % Job title
  {Boson Protocol} % Organization
  {Remote} % Location
  {Jun. 2022 - Sep. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed Solidity smart contracts for EVM using ERC/EIP standards such as Diamond (Multi-Facet Proxy), ERC20, ERC1155, ERC721, and EIP712.}
      \item {Led the protocol integration with auction systems, order books, and AMMs.}
      \item {Managed and maintained production code, collaborating closely with auditors to ensure the highest levels of security and performance.}
      \item {Implemented industry-leading CI/CD methodologies.}
    \end{cvitems}
  }


\cventry
  {Freelancer Blockchain Engineer} % Job title
  {Web3 Services} % Organization
  {Remote} % Location
  {Jul. 2021 - Jun. 2022} % Date(s)
{
    \begin{cvitems}
      \item {Specialized in designing and implementing smart contracts using Hardhat, integrating Chainlink Oracles to increase the reliability and efficiency of decentralized applications.}
    \end{cvitems}
  }

\cventry
  {Back-End Engineer} % Job title
  {Ripio} % Organization
  {Remote} % Location
  {Jul. 2021 - Jun. 2022} % Date(s)
  {
    \begin{cvitems}
      \item {As a member of the Back-End team, actively contributed to the development of new features, bug fixes, and performance enhancements for a monolithic Express.js server.}
      \item {Played a pivotal role in the integration of the back-end with a cutting-edge cryptocurrency trading engine, utilizing Amazon SQS and DynamoDB to enhance transaction processing capabilities.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Full-Stack Software Engineer} % Job title
    {Rocketseat} % Organization
    {Remote} % Location
    {Dec. 2020 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed front-end and back-end solutions utilizing React and Node.js, improving the educational platform in terms of user experience and scalability.}
        \item {Directed a development team, guiding them through scrum ceremonies and ensuring successful project deliveries within designated milestones.}
      \end{cvitems}
    }

\cventry
  {Full-Stack Software Engineer} % Job title
  {Trier Sistemas} % Organization
  {Tubarão, Brazil} % Location
  {Apr. 2019 - Aug. 2020} % Date(s)
  {
    \begin{cvitems}
      \item {Integrated swiftly into the engineering team after an intensive training program, exhibiting quick learning and adaptability.}
      \item {Delivered full-stack solutions in TypeScript, Angular, Java, and Spring, contributing to various high-quality software products.}
      \item {Progressed rapidly from an intern to a mid-level software engineer within a year, demonstrating exceptional growth and skill acquisition.}
    \end{cvitems}
  }

\end{cventries}
